---
title       : Simple Principal Interest Calculator 
subtitle    : Application to calculate Simple Principal Interest
author      : Milan Shrestha
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

This application can be used to calucate Simple Principal Interest.

The formula for Simple Principal Interest is:

     Amount = Principal*( 1+Interest_Rate*Year) 


--- .class #id 

## The ui.R File

* It uses default page Layout.
* Text Fields has been used to enter numeric inputs, Principal,Interest Rate and Years requried for Simple Principal Interest calculations.
```{r results='hide'}
textInput('principal', 'Principal', value = "")
textInput('rate', 'Interest Rate', value = "")
textInput('years', 'years', value = "")
```

* The results are shown as simple text but sufficient for for this purpose.

---

## The server.R File

* Takes the input from client and stores in 3 variables.

```{r eval=FALSE}
output$principal <- renderPrint({as.numeric(input$principal)})
output$rate <- renderPrint({as.numeric(input$rate)})
output$years <- renderPrint({as.numeric(input$years)})
        
```
* calculates and Renders the Output

```{r eval=FALSE}
output$outputValue <- renderText({
            if (input$goButton == 0) "Please click Go button once to start calulating Interest"
            else if (input$goButton >= 1) 
                calculateInterest(as.numeric(input$principal),
                                  as.numeric(input$rate),as.numeric(input$years))
        })
```

---

## Calculation

* Separate function (calcuateInterest) has been created to calculate Interest. 
* This method takes 3 parameters (principal,Interest and years)

```{r eval=FALSE}
calculateInterest <- function(principal, rate, years) {
    principal*(1+rate*years)
}
```

----

## Conclusion

* This is a simple and handy application to calculate Simple Principal Interest.
* This application can also be helpful to demonstrate and learn basis of Shiny application.
* Source Code for the is available at here.

